\texttt Design 3-8-17

### 2017-07-10 designs/C/arxcalibur/paper/template.tex
organized package + updated readme

\begin{abstract}
  We define a block cipher with an N\todo{Block size?}-bit block size and K\todo{Key size?}-bit key size. The design is oriented towards PLATFORM TYPE\todo{Constrained Devices? Consumer CPUs? What architecture/native word sizes?}. The design makes use of certain instruction types or gates. \todo{XOR/AND? ADD/XOR? Multiplication? Modular Exponentiation? Lookup Tables?}\\ 
\end{abstract}

@@

\todo{Explain the motivation for the design described here}

\section{Definitions}
\todo{Define the notation used in this paper}\\
\todo{Define how the state is laid out and indexed/addressed}\\
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left...

>>>>

\begin{abstract}
  We define a block cipher with an 128-bit block size and 128-bit key size. The design is oriented towards general purpose CPUs and software implementation. The design makes use of addition and xor to mix columns, and rotations to shift rows. \\ 
\end{abstract}

@@

In this paper, we define a minimalist ARX based cipher, dubbed "Arxcalibur". It utilizes simple addition and xor to mix the columns of four 32-bit words, and simple rotations to shift the rows. One iteration of the round function consists of just 21 relatively pipeline-friendly instructions, and only two rounds are required for complete diffusion.

We also
\section{Definitions}
\todo{Define the notation used in this paper}\\
\todo{Define how the state is laid out and indexed/addressed}\\
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left...

### 2017-07-10 designs/nonlinear/blockcipher/arx/1/paper/blockcipher.tex
organized package + updated readme

\author{Ella Rose\inst{1}}
\institute{Paso Robles, California \email{python_pride@protonmail.com}}
\title[\texttt Design 3-4-17]{\texttt Design 3-4-17}

@@

\begin{abstract}
  We define and explain the design of a 256-block cipher. The minimalist design is tailored to produce high throughput and low latency on general purpose CPUs, and simple implementation in hardware. Additionally, due to the bit-sliced nature of the design, we predict that it would be reasonably efficient in constrained environments..
\end{abstract}

@@

\section{Introduction}
We describe a cipher algorithm that uses simple XOR, AND, and rotate left instructions on four 64-bit words. Minimum amounts of diffusion are guaranteed through the application of a shift rows and mix column like structure. The 4x4 s-box is the most compact  implementation of all ideal 4x4 s-boxes, and is implemented in 9 instructions. % to do: \cite{http://skew2011.mat.dtu.dk/proceedings/Finding%20Optimal%20Bitsliced%20Implementations%20of%204%20to%204-bit%20S-boxes.pdf}

\section{Definitions}
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left. The state is modeled as a 4x64 grid, with each 64-bit word representing a row. The 64-bit rows will be referred to by $a$, $b$, $c$, and $d$. We define functions in the following section about the algorithm.

\section{Algorithm}
The cipher is an Even-Mansour based construct. It uses a key addition layer, followed by application of a permutation, followed by another key addition layer. The design uses this simple key addition layer, as opposed to generating round keys and applying them after every iteration of the permutation (as is common), because we cannot cite an explicit reason or benefit for so many key application layers. This saves implementation complexity, as there is no key schedule or cacheing of the key schedule.

Each iteration of the permutation consists of alternating linear diffusion and non-linear layers. The diffusion layer consists of three applications of the shift and mix function with differing rotation amounts, which is designed to spread differences around the state evenly. This is followed by the non-linear layer, which is an optimal bitsliced implementation of an optimal 4x4 s-box. The s-box is applied 64 times in parallel on each 4-bit high 1-bit wide section of the state.

Each application of the permutation is preceded by the addition of a round constant. The round constants are generated via a simple function that provides a high degree of difference between outputs.

In psuedocode, the cipher is defined as follows:

\begin{verbatim}
add_key(state, key)
for round_number in 1 ... round_count:
        add_constant(state, round)
        permutation(state)
add_key(state, key)
\end{verbatim}

Next, we will define the $generate\_constant$ function:

\begin{align}
constant := round\_number\\
constant := constant \oplus (constant <<< 3)\\
constant := constant \oplus (constant <<< 6)\\
constant := constant \oplus (constant << 17)\\
constant := constant \oplus (constant << 15)\\
constant := constant \oplus (constant << 24)\\
\end{align}

And the add constant function:

\begin{align}
a = a \oplus generate\_constant(round\_number)
\end{align}

Now we can define the permutation:

%\begin{align}

>>>>

\author{Ella Rose\inst{1}}
\institute{Paso Robles, California \email{python_pride@protonmail.com}}
\title[\texttt Design 2/24]{\texttt Design 2/24}

@@

\begin{abstract}
  We define and explain the design of a 128-block cipher. It is similar in layout and design to Rinjdael, and could be modeled as such with modified linear and s-box layers. The modifications seek to replace one of the slower parts of Rijndael, the mixColumns routine, with an SIMD/parallel friendly routine that is scales well to 8-bit platforms. Additionally, the s-box is replaced with the concatenation of 2 "golden" 4x4 s-boxes. 
\end{abstract}

@@

\section{Introduction}
The Rijndael cipher has proven itself to be well designed. It has remained secure for years, despite seeing immense amounts of cryptanalysis by extremely talented researchers. However, the mixColumns operation is relatively complicated both in implementation and in theory. We describe a design similar to Rijndael that uses a conceptually simpler linear mixing function. This function is dubbed mixState and uses only XOR gates and rotations. It provides full diffusion in one round in a scalable and parallel-friendly manner.

\section{Definitions}
We use $\oplus$ to denote XOR and $\lll$ to denote bitwise rotation left. The state is modeled as a 4x4 grid of 8-bit words. The 32-bit rows will be referred to by $a$, $b$, $c$, and $d$. The 8-bit bytes of the state will be address by $state_i$, where $i$ is the index of the byte in question. We use zero based indexing; The upper most word of a is considered to be $i = 0$, and the least significant word in d is considered to be $i = 15$. We denote the 8-bit s-box as s\_box, while we denote the two 4-bit s-boxes as s\_box4a and s\_box4b.

\section{Algorithm}
The permutation consists of five steps: addKey, addConstant, subBytes, mixState, transposeState. The addKey step is self explanatory, and is implemented using XOR to add the key to the state:

\begin{align}
\displaystyle\sum_{i=0}^{15} state_i \oplus key_i
\end{align}\\

 The addConstant step uses the index, round number, and s-box to produce and apply a constant to each 8-bit word:
\begin{align}
\displaystyle\sum_{i=0}^{15} state_i \oplus s\_box(i + round_i)
\end{align}\\

The subBytes step uses two separate 4x4 s-boxes on each 8-bit word; One s-box is applied to the upper 4 bits, while the other s-box is applied to the lower 4 bits. On a platform that is not space constrained, we simplify the process and concatenate the s-box entries to create an 8x8 s-box. The 8-bit s-box is applied to each 8-bit word:

\begin{align}
\displaystyle\sum_{i=0}^{15} subBytes(state_i)
\end{align}\\

The mixState function alternates between mixing vertical pairs of 8-bit words and shifting the $b$ and $d$ rows. First, we define a central component of mixState, mixPair:

\begin{align}
x := r1_i \\
y := r2_i \\
x := x \oplus y \\
x := x \lll 1 \\
y := y \oplus x \\
y := y \lll 2 \\
x := x \oplus y \\
x := x \lll 4 \\
y := y \oplus x \\
\end{align}

In the above, $r1_i$ and $r2_i$ represents either $a_i$ and $b_i$ or $c_i$ and $d_i$. After the first XOR, each 1x2-bit subsection has been activated. After the first rotation and second xor, each 2x2-bit subsection has been activated. After the second rotation and third xor, each 4x2 bit subsection has been activated. Finally, after the final rotation and  mixPair is a component of the mixPairs function, which applies mixPair to each of the eight pairs of 8-bit words:

### 2017-07-10 designs/nonlinear/blockcipher/arx/1/paper/design.tex
organized package + updated readme

Each application of the permutation is preceded by the addition of a round constant. The round constants are generated via a simple function that provides a high degree of difference between outputs.

@@

\begin{align}
constant := round\_number\\
constant := constant \oplus (constant <<< 3)\\
constant := constant \oplus (constant <<< 6)\\
constant := constant \oplus (constant << 17)\\
constant := constant \oplus (constant << 15)\\
constant := constant \oplus (constant << 24)\\
\end{align}

@@

\begin{align}
a = a \oplus generate\_constant(round\_number)
\end{align}

@@

%\begin{align}

\begin{align}
\displaystyle\sum_{i=0}^{4} mixPair(a_i, b_i), mixPair(c_i, d_i)\\
\end{align}

Inside the mixState function, applications of mixPairs are interleaved with shiftRows instructions, with a final application of mixPairs operating across halves in order to mix the top and bottom rows of the state:

\begin{align}
mixPairs(a, b, c, d)\\
shiftRows(b, d, 1) \\
mixPairs(a, b, c, d) \\
shiftRows(b, d, 2) \\
mixPairs(a, b, c, d) \\
mixPairs(a, c, b, d) \\
\end{align}

After mixState is applied, the words are transposed by feeding the indices into to s\_box4a:

\begin{align}
for\ i\ in\ 0\ ...\ 16:\\
	\quad j = sbox[i] \\
	\quad state_j = state_i \\
\end{align}

>>>>

Each application of the permutation is preceded by the addition of a round constant. The round constants are generated via a simple function that provides a high degree of difference between outputs. Addition of the round constants eliminates rotational symmetry. Without them, inputs that are rotations of each other would produce outputs that are rotations of each other.

@@

\begin{align}
constant := round\_number\\
constant := constant \oplus (constant <<< 3)\\
constant := constant \oplus (constant <<< 6)\\
constant := constant \oplus (constant << 17)\\
constant := constant \oplus (constant << 15)\\
constant := constant \oplus (constant << 24)
\end{align}

@@

\begin{align}
a := a \oplus generate\_constant(round\_number)
\end{align}

@@

\begin{

### 2017-07-10 designs/nonlinear/blockcipher/arx/2/paper/design3817.tex
organized package + updated readme

\begin{abstract}
  We define a substitution-permutation based block cipher with an 256-bit block size and 512-bit key size. The design is oriented towards desktop CPUs and dedicated hardware. The bit sliced design works best with the largest word size available, so we define a variant that utilizes 64-bit words. The design makes use of only XOR/AND gates and rotations. The 4x4 S-Box is calculated discretely each application, and uses the shortest possible number of instructions among all ideal 4x4 S-Boxes.\\ 
\end{abstract}

@@

\section{Introduction}
 Block ciphers are a widely used component in many cryptography schemes. They can be used with a mode of operation to provide confidentiality (as well as authenticity and integrity) to data, they can be combined with a counter to create a secure random number generator, and they can be used as the compression function inside of a hash function. When required, block ciphers can be designed with a smaller state size (80-128 bits) then a hash or stream cipher (160 bits+), which can lead to smaller and less expensive hardware implementations. Block ciphers are a very versatile class of algorithm.

@@

\section{Definitions}
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left. The state consists of four 64-bit words. We denote the four words as $a$, $b$, $c$, and $d$. We refer to the key that is exclusive-or'd into the state as the "Linear Key", and the key that is used for the bit transposition as the "Non-Linear Key". The four 64-bit words of the a key will be referred to as $k0$, $k1$, $k2$, and $k3$. The incrementing counter that is fed to the constant generation function is denoted as $i$\\

We will use the following function names: $K_l$ refers to the linear key addition layer, while $K_n$ refers to the non-linear key addition layer (the keyed bit permutation); $K_f$ refers to the composition of $K_n$ and $K_l$, meaning $K_f(a, b, c, d) \equiv K_l(K_n(a, b, c, d))$. Application of the linear layer is denoted as $L(a, b, c, d)$, while application of the non-linear/S-Box layer is denoted as $S(a, b, c, d)$. The "load" function unpacks a 256-bit key into four 64-bit words.

\section{Algorithm}
 We define a Substitution-Permutation Network type cipher algorithm. The first thing to note is that the algorithm utilizes a non standard key addition layer. The key addition layer consists of two parts; First, a non-linear key addition layer is applied, in the form of a keyed bitwise permutation. Second, a standard linear key addition layer is applied, in the form of exclusive-or with the Linear Key. The key addition layer is applied before/after every four iterations of the permutation.

Each round of the permutation consists of generation and addition of the round constant to the word $a$ of the state via exclusive-or, application of the non-linear layer or "S-Box" to the columns of the state, and lastly the linear branching layer. Two rounds are required for full diffusion; One "step" consists of 4 iterations of the round function, and the key addition layer occurs before/after each step. \\

\begin{algorithmic}
\Function{$encrypt$}{$a, b, c, d, nonlinear\_key, linear\_key$}
	\State $i \gets 0;$
	\For {$step \gets 0; step < 4; step \gets step + 1$}
		\State $a, b, c, d \gets bit\_shuffle(a, b, c, d, nonlinear\_key);$
		\State $a, b, c, d \gets add\_key(a, b, c, d, linear\_ key);$

		\For{$round \gets 0; round < 4; round \gets round + 1;$}	
			\State $a, b, c, d \gets round_function(a, b, c, d, i);$	
			\State $i \gets i + 1$
		\EndFor
	\EndFor
\EndFunction\\
\end{algorithmic}

@@

\begin{algorithmic}
\Function{$bit\_shuffle$}{$a, b, c, d, nonlinear\_key$}
	\State $k0, k1, k2, k3 \gets load(nonlinear\_key)$
	\For{$round \gets 0; round < 2; round \gets round + 1;$}
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 1,\ \ 2,\ \ 3, k0, k1, k2, k3);$
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 4,\ \ 8,\ 12, k0, k1, k2, k3);$
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, 16, 32,\ 48, k0, k1, k2, k3);$
	\EndFor
\EndFunction\\
\end{algorithmic}

@@

\begin{algorithmic}
\Function{$add\_key$}{$a, b, c, d, linear\_key$}
	\State $k0, k1, k2, k3 \gets load(linear\_key)$ % need to clarify k0 and friends are used for linear key to, and define load
	\State $a \gets a \oplus k0$
	\State $b \gets b \oplus k1$
	\State $c \gets c \oplus k2$
	\State $d \gets d \oplus k3$
\EndFunction
\end{algorithmic}

The permutation is composed of three functions: addition of the round constant, the non-linear S-Box layer, and the linear diffusion layer. Each round constant is generated by supplying successive values of an incrementing counter to the constant generation function .

@@

The $generate\_constant$ function is defined as follows: \\

@@

The non-linear S-Box function applies a 4x4 S-Box with ideal cryptographic properties on each of the 64 columns of the state. The S-Box is not evaluated via table lookup, but is computed explicitly upon each invocation. This removes a tming side channel that could otherwise be used to break the algorithm in practice The non-linear S-box addition layer is defined as follows: \\

@@

\section{Design\ Rationale}
The non-linear key addition layer, or keyed bitwise permutation, is designed to thwart algebraic attacks by making it to where the terms of the equations that describe the cipher output are a secret. The transposition may additionally complicate linear and differential cryptanalysis. A software implementation of the bitwise permutation utilizes the choice swap function to conditionally transpose bits according to the key. Because this is a bit sliced operation, it should scale reasonably well across different architectures and word sizes. A hardware implementation has the potential to implement the bitwise permutation via crossed wires, which could save considerable time. The software implementation of the bitwise permutation is not terribly slow, but it does use more instructions then the linear and non-linear parts of the round function. Resistance of the algorithm against related key attacks was not considered; Considering the nature of the transposition operation, it is probable that one could easily find two keys that will take a given input to identical output states. For this reason, combined with the fact that no key schedule is applied to the non-linear key, we do not recommend the usage of this variant as the building block of a compression function.

The linear exclusive-or key addition layer is standard and is used in many if not most (modern) cipher designs. This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate. Additionally, exclusive-or is an involution, which can simplify implementation even more in some cases. \\

@@

@@

\section{Conclusion}
 We define an 256-bit Substitution-Permutation based block cipher with a 512-bit key that is oriented towards 64-bit CPUs and dedicated hardware. Our design uses only simple XORs, ANDs, and rotations, and offers a simple and constant-time implementation. While perhaps not ideal for smaller architectures, the bit-sliced nature of the design indicates that it should scale reasonably well across different architectures and word sizes. We introduce a non-linear key addition layer to attempt to thwart algebraic attacks against the cipher structure.

>>>>

\begin{abstract}
  We define a substitution-permutation based block cipher with an 256-bit block size and 512-bit key size. The design is oriented towards desktop CPUs and dedicated hardware. The bit sliced design works best with the largest word size available, so we define a variant that utilizes 64-bit words. The design makes use of only XOR/AND/OR gates and rotations. The 4x4 S-Box is calculated discretely each application, and uses the shortest possible number of instructions among all ideal 4x4 S-Boxes.\\ 
\end{abstract}

@@

\section{Introduction}
 Block ciphers are a widely used component in many cryptography schemes. They can be used with a mode of operation to provide confidentiality to data, they can be combined with a counter to create a secure random number generator, and they can be used as the compression function inside of a hash function. When required, block ciphers can be designed with a smaller state size (80-128 bits) then a hash or stream cipher (160 bits+), which can lead to smaller and less expensive hardware implementations. Block ciphers are a very versatile class of algorithm.

@@

\section{Definitions}
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left. The state consists of four 64-bit words. We denote the four words as $a$, $b$, $c$, and $d$. We refer to the key that is exclusive-or'd into the state as the "Linear Key", and the key that is used for the bit transposition as the "Non-Linear Key". The four 64-bit words of a key will be referred to as $k0$, $k1$, $k2$, and $k3$; which key will be clear from the context. The incrementing counter that is fed to the constant generation function is denoted as $i$\\

We utilize a helper function: The "load" function unpacks a 256-bit key into four 64-bit words.

\section{Algorithm}
 We define a Substitution-Permutation Network type cipher algorithm. The first thing to note is that the algorithm utilizes a non standard key addition layer. The key addition layer consists of two parts; First, a non-linear key addition layer is applied, in the form of a keyed bitwise permutation. Second, a standard linear key addition layer is applied, in the form of exclusive-or with the Linear Key. The key addition layer is applied before every four iterations of the permutation, with one additional key application after the last iteration of the permutation.

Each round of the permutation consists of generation and addition of the round constant to the word $a$ of the state via exclusive-or, application of the non-linear layer or "S-Box" to the columns of the state, and lastly the linear branching layer. Two rounds are required for full diffusion; One "step" consists of 4 iterations of the round function, and the key addition layer occurs before each step. \\

\begin{algorithmic}
\Function{$encrypt$}{$message, nonlinear\_key, linear\_key$}
	\State $i \gets 1;$
	\State $a, b, c, d \gets load(message)$
	\For {$step \gets 0; step < 4; step \gets step + 1$}
		\State $a, b, c, d \gets bit\_shuffle(a, b, c, d, nonlinear\_key);$
		\State $a, b, c, d \gets add\_key(a, b, c, d, linear\_ key);$

		\For{$round \gets 0; round < 4; round \gets round + 1;$}	
			\State $a, b, c, d \gets round\_function(a, b, c, d, i);$	
			\State $i \gets i + 1$
		\EndFor
	\EndFor
\EndFunction\\
\end{algorithmic}

@@

\begin{algorithmic}
\Function{$bit\_shuffle$}{$a, b, c, d, nonlinear\_key$}
	\State $k0, k1, k2, k3 \gets load(nonlinear\_key)$
	\For{$round \gets 0; round < 2; round \gets round + 1;$}
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 1,\ \ 2,\ \ 3, k0, k1, k2, k3);$
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 4,\ \ 8,\ 12, k0, k1, k2, k3);$
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, 16, 32,\ 48, k0, k1, k2, k3);$
	\EndFor
\EndFunction\\

\Function{$shift\_and\_shuffle$}{$a, b, c, d, r1, r2, r3, k0, k1, k2, k3$}
	\State $b, c, d \gets shift\_rows(b, c, d, r1, r2, r3)$
	\State $a, b, c, d \gets shuffle\_columns(a, b, c, d, k0, k1, k2, k3)$
\EndFunction\\

\Function{$shuffle\_columns$}{$a, b, c, d, k0, k1, k2, k3$}
	\State $a, c \gets choice\_swap(k0, a, c)$
	\State $b, d \gets choice\_swap(k1, b, d)$
	\State $c, b \gets choice\_swap(k2, c, b)$
	\State $d, a \gets choice\_swap(k3, d, a)$
\EndFunction\\

\Function{$choice\_swap$}{$a, b, c$}
	\State $t \gets b$
	\State $b \gets choice(a, b, c)$
	\State $c \gets choice(a, c, t)$
\EndFunction\\

\Function{$choice$}{$a, b, c$}
	\State $c \oplus (a \land (b \oplus c))$
\EndFunction\\
\end{algorithmic}

@@

\begin{algorithmic}
\Function{$add\_key$}{$a, b, c, d, linear\_key$}
	\State $k0, k1, k2, k3 \gets load(linear\_key)$
	\State $a \gets a \oplus k0$
	\State $b \gets b \oplus k1$
	\State $c \gets c \oplus k2$
	\State $d \gets d \oplus k3$
\EndFunction
\end{algorithmic}

The permutation is composed of three functions: addition of the round constant, the non-linear S-Box layer, and the linear diffusion layer. Each round constant is generated by supplying successive values of an incrementing counter to the constant generation function.

@@

The $generate\_constant$ function ensures an avalanche effect occurs by ensuring one half of the bits of the input word influence one half of the bits of the output word. Each exclusive-or with a rotation of the word doubles the number of bits that influence each bit. After 5 iterations, each output bit is influenced by 32 input bits.\\

@@

The non-linear S-Box function applies a 4x4 S-Box with ideal cryptographic properties on each of the 64 columns of the state. The S-Box is not evaluated via table lookup, but is computed explicitly upon each invocation. This removes a tming side channel that could otherwise be used to break the algorithm in practice The non-linear S-box addition layer is defined as: \\

@@

\section{Design\ Rationale}
The non-linear key addition layer, or keyed bitwise permutation, is designed to thwart algebraic attacks by making it to where the terms of the equations that describe the cipher output are a secret. The transposition may additionally complicate linear and differential cryptanalysis. A software implementation of the bitwise permutation utilizes the choice swap function to conditionally transpose bits according to the key. Because this is a bit sliced operation, it should scale reasonably well across different architectures and word sizes. A hardware implementation dedicated to a single key has the potential to implement the bitwise permutation via crossed wires, which could save considerable time. The software implementation of the bitwise permutation is not terribly slow, but it does use more instructions then the linear and non-linear parts of the round function. Resistance of the algorithm against related key attacks was not considered; Considering the nature of the transposition operation, it is probable that one could easily find two keys that will take a given input to identical output states. For this reason, combined with the fact that no key schedule is applied to the non-linear key, we do not recommend the usage of this variant as the building block of a compression function.

The linear exclusive-or key addition layer is standard and is used in many if not most modern cipher designs. This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate for no real benefit. Additionally, exclusive-or is an involution, which can simplify implementation even more in some cases.

@@

The key size is not 512 bits in length because we target or claim a 512-bit security level; It is 512 bits in length to facilitate the simplest implementation possible. Using the linear key as the non-linear key can modify the properties of the transposition layer, so we chose to use two separate keys. Considering the lack of key schedule and the inability to derive additional key material from a single key, we are left with the only choice of using two separate 256-bit keys.

@@

\section{Attacks}
In this section we will lay out basic attacks against simplified versions of the cipher. We use the term "unknown" to mean a message or key bit whose value is not known. We use the term "unspecific" to mean a message or key bit whose index within the state is not known.

By itself, the non-linear key addition layer can be broken without needing to recover the actual key in block-size (256) chosen plaintexts. Simply encrypt successive powers of 2, or, viewed another way, encrypt each possible word of weight 1. The corresponding ciphertext reveals the destination that the one input bit was transposed to. This attack applies against this weakened variant regardless of the number of rounds.

Adding the linear key layer afterwards, such that our target is now the composition of the key addition layers, we may obtain the linear key by encrypting a block of 0s. The transposition has no effect, and the exclusive-or with the block of 0s leave just the key value. We may then obtain the equivalent information in place of the nonlinear key by the attack mentioned previously. This attack works against this weakened variant regardless of the number of rounds.

Applying the linear diffusion layer after the composed key addition layer, we obtain output where each bit is represented as the exclusive-or sum of some unknown/unspecified key bits and some known but unspecificied input bits. Because the diffusion step is linear, we can still simply encrypt a block of 0s to obtain and obtain the diffused linear key. With this diffused key we can proceed with the encrypt powers of 2 attack to again obtain the key-equivalent information for the keyed transposition. Addition of the round constants will not prevent this attack from succeeding. This attack works against this weakened variant regardless of the number of rounds - the output will always simply be an exclusive-or sum or unknown/unspecified key bits, and some unspecified input bits.

We would like to note that the above attacks would apply regardless of the implementation of the functions - using a different linear diffusing function can not ever solve the above issues, and the attacks do not indicate a failure of any of the involved functions. The attack utilizes only the linear nature of the produced equations. This is the reason why non-linearity is required in a cipher. While the keyed bit shuffle is implemented using AND gates, it only transposes bits and does not influence their value; it effectively just shuffles the terms of the equation.

Now, we will try attacking the composition of the keyed bit shuffle and the application of the s-box.

\section{Conclusion}
 We define an 256-bit Substitution-Permutation based block cipher with a 512-bit key that is oriented towards 64-bit CPUs and dedicated hardware. Our design uses only simple XOR/AND/OR and rotations, and offers a simple and straightforward constant-time implementation. While perhaps not ideal for smaller architectures, due to the large words and state, the bit-sliced nature of the design indicates that it should scale reasonably well across different architectures and word sizes. We introduce a non-linear key addition layer to attempt to thwart algebraic attacks against the transparent algebraic structure. Lastly, we include some basic attacks against weakend versions of the cipher.
